Approximation as Differentiation notes

### 2025-02-10 notes.tex
Brackets for function application.

%\geometry{paperwidth=8.3in, paperheight=11.7in}

@@

\begin{definition}[Reindexing functor]
For any $X \in \Fam(J,C)$ and $f: I \to J$ define $X[f] \in \Fam(I,C)$ where $X[f]_i = X_{fi}$.
\end{definition}

@@

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are the bounded lattices;
\item morphisms $f \vdash g: L \to L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq fx \iff gy \leq x$ for any $x \in L$ and any
$y \in L'$.
\end{itemize}

>>>>

@@

\begin{definition}[Reindexing functor]
For any $X \in \Fam(J,C)$ and $f: I \to J$ define $X[f] \in \Fam(I,C)$ where $X[f]_i = X_{f(i)}$.
\end{definition}

@@

Define the category $\LatGal$ where:
\begin{itemize}
\item objects $L$ are the bounded lattices;
\item morphisms $f \vdash g: L \to L'$ are meet-semilattice homomorphisms $f: L \to L'$ paired with
join-semilattice homomorphisms $g: L' \to L$ satisfying $y \leq f(x) \iff g(y) \leq x$ for any $x \in L$ and any
$y \in L'$.
\end{itemize}
